\documentclass[conference]{IEEEtran}

% All these packages you need, if you need any others you can add them here.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{hyperref}

% Reduce aggressive end-of-line hyphenation so the prose reads more naturally.
\pretolerance=10000
\hyphenpenalty=9000
\exhyphenpenalty=9000
\emergencystretch=2em

% Do not change the bibliography style.
\bibliographystyle{IEEEtran}

% ── Project Data ──────────────────────────────────────────────────────────────
% TODO: Confirm full legal names for Khang and Zachary before submission.
\title{Evaluating LLM-Based and Rule-Based Adaptive Mental Health\\
       Questionnaires: A Human-Centric User Study}

\author{
  \IEEEauthorblockN{Jaeyun Ree, Khang Nguyen, Zachary Yeap}
  \IEEEauthorblockA{Department of Software Systems and Cybersecurity\\
                    Faculty of Information Technology, Monash University}
}
% ─────────────────────────────────────────────────────────────────────────────

\begin{document}

\maketitle

% ── Abstract ─────────────────────────────────────────────────────────────────
\begin{abstract}
% TODO: ~150 words
% Hint: Cover (1) problem: static questionnaires fail to reflect changing conditions,
%       (2) approach: Navigator prototype with rule-based and LLM-based methods,
%       (3) study: within-subjects user study, metrics: Clarity / Quality / Relevance,
%       (4) key findings.
\end{abstract}

% ── Section 1: Introduction ───────────────────────────────────────────────────
\section{Introduction}
\label{sec:intro}

Mental health is increasingly recognised as a critical component of overall well-being,
and digital health applications are playing a growing role in routine screening and
self-monitoring. In practice, most of these applications rely on standardised static
instruments such as the PHQ-9 \cite{kroenke2001} and the GAD-7 \cite{spitzer2006},
which present the same fixed set of items at every check-in regardless of the user's
current condition, prior responses, or longitudinal history. While these instruments
are clinically validated, their rigid format can feel repetitive and burdensome, and
often fails to reflect how a person's mental state evolves over time
\cite{malanin2025}.

Adaptive questionnaire techniques, such as branching logic and computerised adaptive
testing, have been introduced to partially address this limitation by tailoring item
sequences to user input \cite{wang2023}. However, these rule-based mechanisms remain
bounded by predefined decision trees and cannot generate new items or reframe questions
based on a user's individual context. Recent advances in Large Language Models (LLMs)
open a new design space for adaptive assessment: LLMs can synthesise context-aware
questions informed by a user's health profile and prior responses, and have begun to
be explored as engines for patient-reported outcome measures \cite{terheyden2025}.

Despite this promise, the use of LLMs in mental health remains at an early stage. A
recent systematic review of mental health chatbots highlights that most existing systems
are still rule-based, and that LLM-based designs, while more flexible, introduce
new concerns around safety, appropriateness, and clinical reliability
\cite{hua2025, li2025llm, shen2026}. To our knowledge, no prior work has directly
compared rule-based and LLM-based adaptive mental health questionnaires within a
single unified application using a controlled, human-centric evaluation.

To address this gap, we developed \emph{Navigator}, a web-based prototype that
implements two distinct monthly mental health check-in methods within the same
application environment:
\begin{itemize}
  \item \textbf{Rule-based method:} predefined branching logic determines which
        follow-up questions appear based on fixed risk-level thresholds.
  \item \textbf{LLM-based method:} Google Gemini 2.5 Flash dynamically generates
        personalised questions from the user's health profile and prior assessment data.
\end{itemize}
Using a within-subjects study design, participants interacted with both methods via a
standardised persona (Sophie) and completed a structured feedback survey. Evaluation
metrics are grounded in the COSMIN content-validity framework \cite{terwee2018},
which identifies \emph{Clarity}, \emph{Quality}, and \emph{Relevance} as core
dimensions of questionnaire content validity.

This study aims to answer the following research questions:
\begin{itemize}
  \item \textbf{RQ1 (Clarity):} Do LLM-generated questionnaires produce higher perceived
        clarity than rule-based questionnaires?
  \item \textbf{RQ2 (Quality):} Do LLM-generated questionnaires produce higher perceived
        quality than rule-based questionnaires?
  \item \textbf{RQ3 (Relevance):} Do LLM-generated questionnaires produce higher perceived
        relevance than rule-based questionnaires?
\end{itemize}

The main contributions of this work are:
(1) the Navigator prototype, a Flutter web application implementing both rule-based
and LLM-based adaptive questionnaires within a unified interface;
(2) a within-subjects user study design using a standardised persona to ensure fair
comparison across conditions; and
(3) an empirical, COSMIN-grounded evaluation of user perceptions of Clarity, Quality,
and Relevance for LLM-based versus rule-based adaptive mental health questionnaires.

The remainder of this paper is organised as follows.
Section~\ref{sec:related} reviews related work on mental health questionnaire systems,
LLMs in healthcare, and adaptive survey design.
Section~\ref{sec:system} presents the methodology, covering the research
approach, system design, controlled scenario, study design, and
evaluation metrics.
Section~\ref{sec:results} presents the results, followed by discussion in
Section~\ref{sec:discussion}, and conclusions in Section~\ref{sec:conclusion}.

% ── Section 2: Related Work ───────────────────────────────────────────────────
\section{Related Work}
\label{sec:related}

Although the broader Navigator project was initially framed around adaptive
assessment across multiple chronic-disease domains \cite{aihw2012}, this paper
narrows the evaluation to mental health check-ins, which provide a concrete,
high-impact, and survey-feasible context for comparing rule-based and LLM-based
adaptation methods. We accordingly organise prior work along three lines that
progressively narrow toward our research question. We first review the dominant
paradigm of static, validated mental health instruments and the limitations
they impose on longitudinal self-report. We then survey existing adaptive
questionnaire strategies, from computerised adaptive testing to rule-based
interface adaptation, and most recently to LLM-generated patient-reported
outcome measures. Finally, we examine the emerging body of work on LLM-based
mental health systems, identifying both their promise and the safety
considerations that constrain their design. We conclude by introducing the
COSMIN content-validity framework \cite{terwee2018}, which provides the three
evaluation dimensions used in this study.

\subsection{Mental Health Assessment and Static Instruments}
\label{subsec:rw_static}

Mental health screening in primary care and digital health applications has
long relied on standardised, fixed-item self-report instruments. The Patient
Health Questionnaire-9 (PHQ-9) for depression \cite{kroenke2001} and the
Generalised Anxiety Disorder-7 (GAD-7) scale \cite{spitzer2006} remain
among the most widely used tools, demonstrating strong sensitivity and specificity
(both 88\% for PHQ-9 $\geq 10$; 89\% and 82\% for GAD-7 $\geq 10$) and
providing interpretable severity cut-offs across diverse populations. Their
brevity, transparency, and validated scoring make them attractive for
integration into digital platforms aimed at routine, longitudinal mental
health monitoring.

However, the very stability that gives these instruments their psychometric
Strength also imposes meaningful limitations on user experience. Static
questionnaires repeat the same items at every administration, regardless of a
user's current state or response history. Repeated exposure to identical
wording can lead to response fatigue and reduced engagement, particularly in
longitudinal self-report scenarios where users complete the same scale weekly
or monthly \cite{gibbons2008, choi2010, malanin2025}. Ecological momentary assessment studies have
documented this problem directly: in a 28-day smartphone-based depression
study, only seven of eleven participants completed the full protocol and the
average daily response rate was 62.5\% \cite{maatoug2021}, suggesting that
Repeated digital self-report can suffer from engagement and completion issues
challenges, even when the underlying measures are clinically meaningful.

Beyond engagement, fixed wording can raise concerns about content validity.
Baas et al.\ \cite{baas2011} demonstrated that one PHQ-9 item exhibited measurement
non-invariance across ethnic groups, revealing cultural bias in supposedly
universal items. Wild et al.\ \cite{wild2005} similarly argues that questionnaire wording
must be treated as a structured design and validation problem rather than a
literal translation. These findings indicate that even well-validated
instruments carry implicit assumptions about who the respondent is and how
they interpret each item. Adaptive systems may help identify and mitigate these
assumptions through more context-sensitive wording and item selection.

\subsection{Adaptive Questionnaire Approaches}
\label{subsec:rw_adaptive}

To mitigate the burden and rigidity of static instruments, prior work has
explored adaptive questioning strategies. The most established approach is
Computerised Adaptive Testing (CAT), which uses item response theory to select
The most informative items based on prior responses. Gibbons et al.\ \cite{gibbons2008}
demonstrated that the CAT-based assessment of mood and anxiety disorders reduced
the number of administered items by approximately 95\% relative to a full
item bank, while preserving strong correlation with the full-scale score.
Choi et al.\ \cite{choi2010} likewise compared static short forms, two-stage branching,
and CAT against the full PROMIS depression item bank, finding that CAT
outperformed static short forms on most performance criteria, with two-stage
semi-adaptive testing approaching CAT-level performance.

A parallel line of work has examined rule-based adaptive interfaces in broader
health contexts. In a systematic review of adaptive user interfaces for
chronic disease, Wang et al.\ \cite{wang2023} identify three dominant adaptation
strategies: rule-based ``if--then'' logic, machine-learning-driven prediction,
and feedback-loop systems that revise content based on accumulating user
data. Although rule-based approaches dominate the surveyed literature due to
Their interpretability and low computational overhead, they are bounded by
The comprehensiveness of their predefined rules prevents them from adapting to contexts
The designer did not anticipate. Closed-loop systems, which integrate
continuous data collection with iterative refinement remains comparatively
rare \cite{brown2022}.

A more recent direction extends adaptation beyond item selection toward item
generation. Terheyden et al.\ \cite{terheyden2025} introduces the concept of LLM-powered
Patient-Reported Outcome Measures (LLM-PROMs), in which large language models
generate personalised open-ended items and interpret responses against
established psychometric scaffolds. Their framework argues that LLM-based
PROMs should be developed from validated content and benchmarked against
fixed instruments to preserve content validity. This conceptual shift, from
\emph{selecting} items in a finite bank to \emph{generating} items
conditioned on user context, defines the design space we examine in this
paper. Unlike CAT, which adapts by selecting from a validated item bank,
LLM-based methods can also alter wording or generate new follow-up prompts,
creating both opportunities for personalisation and additional risks for
validity.

\subsection{LLM-Based Systems in Mental Health}
\label{subsec:rw_llm_mh}

The emergence of large language models has accelerated interest in
conversational and adaptive mental health tools, but evidence on their
efficacy and safety remains preliminary. In the most comprehensive review to
date, Hua et al.\ \cite{hua2025} surveyed 160 mental health chatbot studies published
between 2020 and 2024, classifying them as rule-based, machine-learning-based,
or LLM-based. Their analysis reveals an important asymmetry: although LLM-based
Systems grew rapidly in 2024, they remain concentrated in early-stage
validation, while rule-based systems still dominate later-stage human and
clinical testing. This positioning motivates our study as a pilot, user-centred
feasibility evaluation rather than a clinical efficacy trial.

User-facing evidence further suggests that LLM behaviour in mental health is
highly condition-dependent. Li et al.\ \cite{li2025llm} analysed 112{,}698 social-media
posts about LLM use for mental health and found that sentiment varied
substantially across conditions: users with ADHD and ASD reported strongly
positive experiences (sentiment scores of 0.722 and 0.557 respectively),
whereas schizophrenia-spectrum discussions reported strongly negative
sentiment ($-0.569$), often describing chatbot responses that appeared to
intensify delusional thinking. Complementing this, Shen et al.\ \cite{shen2026} conducted
a clinician-blind evaluation of multiple LLM versions on 158 prompts and found
that no tested model reliably produced appropriate responses to psychotic
content. Together, these findings establish two requirements for any LLM-based
mental health tool: condition-aware framing and explicit safety boundaries.
This distinction is also important for our setting: questionnaire systems do
not aim to provide therapeutic dialogue, but rather to elicit structured,
interpretable self-reports through clear and relevant prompts. The risks
identified in conversational LLM use therefore translate, but do not transfer
directly, into the design constraints for LLM-generated questionnaire items.

Despite this growing body of work, limited prior research has directly
compared rule-based and LLM-based adaptive questionnaires within a unified
application using a controlled, within-subjects evaluation. Existing
comparisons either contrast different chatbot generations against one another
\cite{hua2025}, study LLM use in unstructured user discussions
\cite{li2025llm}, or evaluate adaptive item \emph{selection} without
addressing LLM-generated \emph{wording} \cite{gibbons2008, choi2010}. Our
work addresses this gap by holding the application environment, the evaluation
persona, and the participant group constant, thereby isolating the effect of
the adaptation method itself.

\subsection{Evaluation Framework: Content Validity via COSMIN}
\label{subsec:rw_cosmin}

To evaluate the two adaptation methods on common ground, we adopt the COSMIN
content-validity framework \cite{terwee2018}. Drawing on an international
Delphi study of 159 experts, COSMIN formalises content validity along three
dimensions: \emph{relevance}, \emph{comprehensiveness}, and
\emph{comprehensibility}, for the target population and context of use. We
map these directly onto the three evaluation metrics used in this paper:
\emph{comprehensibility} corresponds to \emph{Clarity} (whether the wording is
easy to understand), \emph{relevance} corresponds to \emph{Relevance} (whether
the items fit the participant's context), and \emph{comprehensiveness}
corresponds to perceived \emph{Quality}, since participants are asked to
judge whether each adaptive question appears complete, appropriate, and
useful within the monthly mental-health check-in context (see
Section~\ref{subsec:metrics}). This grounding provides a principled basis for
comparing rule-based and LLM-based adaptive questionnaires that draws on
established patient-reported-outcome methodology rather than ad-hoc usability
heuristics.

% ── Section 3: Methodology ───────────────────────────────────────────────────
\section{Methodology}
\label{sec:system}

This section presents the end-to-end methodology used in this study.
The research proceeded through six stages: (1)~a literature review of
static and adaptive mental health instruments to identify the limitations
that motivate this work (Section~\ref{sec:related}); (2)~identification
of validated questionnaire items, drawing primarily on the PHQ-9
\cite{kroenke2001} and GAD-7 \cite{spitzer2006}, and a decision to
focus the evaluation on the mental health domain; (3)~design and
implementation of two adaptation methods, rule-based and LLM-based,
within a unified web-based prototype
(Sections~\ref{subsec:architecture}--\ref{subsec:llm_based});
(4)~construction of a controlled evaluation scenario using a standardised
persona (Section~\ref{subsec:sophie}); (5)~design of a within-subjects
user study with a COSMIN-grounded feedback survey
(Sections~\ref{subsec:research_design}--\ref{subsec:metrics}); and
(6)~data collection and analysis (Section~\ref{sec:results}).

The prototype was designed as an evaluation instrument rather than a
production system: its purpose is to present both methods within a
single, controlled application environment so that user perceptions can
be compared fairly. Architectural choices, including a shared interface, fixed
persona, and identical health domains, were therefore driven by the
evaluation design.

\subsection{Architecture Overview}
\label{subsec:architecture}

Navigator is implemented as a Flutter web application backed by Supabase
(PostgreSQL) for question storage and branching-rule definitions. A
single-page interface presents foundational intake questions, monthly
check-ins for six health domains (Mental Health, Dietary, Physical
Activity, Alcohol, Smoking/Vaping, and Women's Health), and a results
dashboard. Although the broader prototype supports all six domains, the
present study evaluates only the Mental Health monthly check-in pathway,
which provides a concrete and high-impact context for comparing
adaptation methods. Both the rule-based and LLM-based monthly check-in methods
share the same front-end layout, question rendering components, and
scoring pipeline, so that any difference participants observe can be
attributed to the adaptation method itself rather than to interface
variation.

For LLM-based question generation, the application calls the Google
Gemini~2.5 Flash API. This model was selected for its low latency and
structured-output support (native JSON response mode), which are
practical requirements for generating questionnaire items in real time
within a web application. A deterministic fallback path returns
pre-authored enhanced questions if the API is unavailable, ensuring that
every participant in the study receives the same enhanced questionnaire
content regardless of network conditions.

\subsection{Rule-Based Method}
\label{subsec:rule_based}

The rule-based method adapts monthly check-in questionnaires through a
branching engine that evaluates predefined conditional rules after each
user response. Each rule is a triple of \emph{trigger question},
\emph{boolean expression}, and \emph{target action}. When a user answers
the trigger question, the engine evaluates the expression against the
response value; if the condition is met, the target questions are shown
or hidden accordingly. This approach mirrors the ``if--then'' rule-based
adaptation strategy identified as the dominant paradigm in chronic-disease
adaptive interfaces \cite{wang2023}.

Rules operate on single-question, single-timepoint data: a rule can
reference the current answer to one question but cannot access prior
month responses or aggregate longitudinal patterns. For the Mental Health
domain, risk levels are classified at the domain level using
project-specific percentage-based thresholds loosely inspired by the
PHQ-9 severity bands \cite{kroenke2001}: scores below 25\% of the
domain maximum are classified as \emph{None}, 25--50\% as \emph{Mild},
50--75\% as \emph{Moderate}, and above 75\% as \emph{High}. These
thresholds are a simplified mapping for the prototype and do not
correspond directly to the validated PHQ-9 cut-off scores.

A concrete example illustrates the method's limitation.
Table~\ref{tab:comparison} lists the mental health questions presented
under each method in Sophie's scenario
(Section~\ref{subsec:sophie}). Under the rule-based method, Rule~13
specifies that the functional-impact question is shown only when the mood
frequency response is $\geq 2$ on a 0--3 scale. Sophie's Month~2
response of~1 (``Several days'') does not meet this threshold, so the
functional-impact item remains hidden, even though two consecutive
months of Mild risk may warrant exploring it. The rule-based system
cannot detect this longitudinal pattern because each rule evaluates a
single response in isolation.

\subsection{LLM-Based Method}
\label{subsec:llm_based}

The LLM-based method generates personalised monthly check-in questions by
conditioning a large language model on the user's prior health snapshot.
At the start of a monthly check-in, the system constructs a structured
prompt containing two inputs: (1)~a \emph{UserSeed}, a versioned summary of
the user's demographics, domain-level risk
classifications, and free-text context notes from the previous assessment
period; and (2)~the baseline rule-based questions for the current domain,
so the model understands what it is improving upon.

The prompt instructs the model to produce questions that are
\emph{more relevant, clearer, and less repetitive} than the rule-based
baseline, grounding the generation task in the same content-validity
dimensions (Clarity, Quality, Relevance) used in the evaluation
(Section~\ref{subsec:metrics}). The model returns a JSON array of
question objects, each containing the question text, response options, and
a brief rationale for the adaptation. Generation uses a low temperature
setting ($T = 0.3$) to favour consistency and structured output over
creative variation.

This design aligns with the LLM-PROM framework proposed by Terheyden
et~al.\ \cite{terheyden2025}, which argues that LLM-generated
patient-reported outcome items should be developed from validated content
and benchmarked against fixed instruments. In Navigator, the LLM does not
generate questions from scratch; it \emph{transforms} the existing
validated baseline questions using the user's longitudinal context.
Table~\ref{tab:comparison} presents the five specific transformations
applied in Sophie's scenario: history-aware rephrasing of the mood
frequency item, occupation-specific language for the manageability item,
a new trend-direction item that captures the two-month persistent Mild
pattern, early unlocking of the functional-impact item based on
longitudinal rather than single-month thresholds, and omission of the
isolation item where Month~1 data showed no change was expected.

\begin{table*}[t]
\caption{Mental health check-in questions under each adaptation method for Sophie's Month~2 scenario. The rule-based column shows the questions produced by the branching engine; the LLM-based column shows the Gemini-generated transformations. Dashes indicate items not presented.}
\label{tab:comparison}
\centering
\small
\begin{tabular}{@{}p{1.6cm}p{3.8cm}p{4.2cm}p{4.6cm}@{}}
\toprule
\textbf{Item} & \textbf{Rule-Based} & \textbf{LLM-Based} & \textbf{Transformation Rationale} \\
\midrule
Mood frequency
& ``In the past month, how often have you felt low mood, sad, hopeless, nervous, worried, or restless?''
& ``Over the past month, have you continued to experience feelings like low mood, worry, or restlessness? Last month you reported this happening on several days.''
& References Month~1 history; acknowledges continuity rather than repeating identical wording. \\
\addlinespace
Managing life
& ``\ldots how often have you felt that important things in your life were difficult to manage?''
& ``\ldots has it felt harder than usual to stay on top of your studies, daily responsibilities, or relationships?''
& Replaces generic ``important things'' with student-specific language. \\
\addlinespace
Trend direction
& Not asked
& ``Since you've reported similar feelings for two months in a row, how would you describe the change over the past month?''
& New item capturing longitudinal signal (two-month Mild pattern) that rule-based thresholds cannot detect. \\
\addlinespace
Functional impact
& \emph{Hidden} because the mood score of~1 does not meet the $\geq 2$ threshold required by the branching rule.
& ``Have these feelings made it harder for you to manage your daily life, for example, attending classes, completing work, or maintaining relationships?''
& Unlocked early based on persistent pattern; phrasing adapted to student context. \\
\addlinespace
Isolation
& ``In the past month, how often do you feel isolated from others?''
& \emph{Skipped} because the Month~1 score was low and stable, so no new information was expected.
& De-prioritises items unlikely to yield new signal, reducing respondent burden. \\
\bottomrule
\end{tabular}
\end{table*}

\subsection{Controlled Scenario: Sophie}
\label{subsec:sophie}

To enable a fair within-subjects comparison, both methods are evaluated
using a single standardised persona rather than participants' own health
data. ``Sophie'' is a fictional 24-year-old female East Asian
international university student whose Month~1 foundational assessment
produced a Mild mental health risk classification and None across all
other domains. Her context notes record specific response details: a mood
frequency score of~1 (``Several days''), a low and stable isolation
score, and no triggered functional-impact questions.

The decision to use a fixed persona serves three evaluation purposes.
First, it eliminates between-participant variation in health profiles,
ensuring that every participant sees the same rule-based and LLM-based
questionnaire outputs and that observed differences in Clarity, Quality,
and Relevance ratings reflect the adaptation method rather than
individual health circumstances. Second, it avoids the ethical
complications of collecting real mental health data in a prototype
evaluation context. Third, it provides a scenario that concretely
illustrates the limitation of rule-based adaptation: Sophie's profile
is designed so that the branching rule's hard threshold blocks the
functional-impact question despite a clinically meaningful two-month
pattern (see Table~\ref{tab:comparison}), creating a clear point of
contrast for participants to evaluate.

The persona was designed with attention to measurement validity
considerations identified in prior work. Baas et~al.\ \cite{baas2011}
demonstrated that PHQ-9 responses can exhibit measurement non-invariance
across demographic groups, and Wild et~al.\ \cite{wild2005} emphasised
that questionnaire wording must account for cultural context. Sophie's
profile, an East Asian international student, was therefore chosen
to represent a demographic for whom culturally adapted wording (as
produced by the LLM method) might be particularly relevant, while
remaining relatable to the predominantly university-aged participant pool.

% ── Study Design (subsections within Methodology) ────────────────────────────
\subsection{Research Design}
\label{subsec:research_design}
\label{sec:study}
% TODO: ~0.2 page
% Cover: within-subjects design, with all participants experiencing both methods,
%        order counterbalanced to mitigate order effects.

\subsection{Participants}
\label{subsec:participants}
% Cover: 18+ years old, university students and working professionals,
%        recruited via Monash forums and LinkedIn,
%        exclusion: Malaysian and Indonesian participants (ethics restriction),
%        target N < 50 per group.

\subsection{Procedure}
\label{subsec:procedure}
% TODO: ~0.3 page
% Cover: Step 1, Foundational Assessment (baseline health profile),
%        Step 2a, Rule-based Monthly Check-In,
%        Step 2b, LLM-based Monthly Check-In,
%        Step 3, Feedback survey (Google Form, Sections A--D),
%        estimated total time: 10--15 minutes.

\subsection{Evaluation Metrics}
\label{subsec:metrics}
% TODO: ~0.2 page
% Cover: 5-point Likert scale for each metric,
%        Clarity: question wording is clear and easy to understand,
%        Quality: questions are well-formed and meaningful,
%        Relevance: questions are relevant to the participant's health context.
%        Also: open-ended questions for qualitative feedback.

% ── Section 5: Results and Analysis ──────────────────────────────────────────
\section{Results and Analysis}
\label{sec:results}

\subsection{Participant Demographics}
\label{subsec:demographics}
% TODO: Summarise age, occupation, gender distribution of final sample.

\subsection{Quantitative Results}
\label{subsec:quant}
% TODO: Report mean Likert scores (Clarity / Quality / Relevance)
%       for Rule-based vs.\ LLM-based.
%       Include Table: mean $\pm$ SD per metric per method.
%       Statistical test (e.g., Wilcoxon signed-rank or paired t-test).

\subsection{Qualitative Findings}
\label{subsec:qual}
% TODO: Thematic analysis of open-ended responses.
%       Key themes: personalisation, question relevance, wording clarity,
%       perceived usefulness.

\subsection{Comparative Analysis}
\label{subsec:comparison}
% TODO: Side-by-side comparison of both methods across all three metrics.
%       Highlight where LLM-based outperforms / underperforms rule-based.

% ── Section 6: Discussion ─────────────────────────────────────────────────────
\section{Discussion}
\label{sec:discussion}

\subsection{Interpretation of Results}
\label{subsec:interpretation}
% TODO: Relate findings back to RQ1--RQ3.
%       Discuss why LLM-based may/may not outperform rule-based on each metric.

\subsection{Limitations}
\label{subsec:limitations}
% TODO:
%   - Small sample size (< 50 per group)
%   - Prototype fidelity (mock persona Sophie, not real patient data)
%   - Single LLM provider (Gemini 2.5 Flash)
%   - 1-D health snapshot; does not capture full longitudinal history
%   - Self-reported metrics (perception, not clinical outcome)

% ── Section 7: Conclusion ─────────────────────────────────────────────────────
\section{Conclusion}
\label{sec:conclusion}
% TODO: ~0.3 page
% Summarise: problem, approach, key findings, implications for adaptive
% health questionnaire design.

\subsection*{Future Work}
% TODO:
%   - Real patient data integration (beyond mock persona)
%   - Longitudinal study across multiple monthly check-ins
%   - Multiple LLM providers comparison
%   - Clinical validation of question quality with domain experts

% ── References ────────────────────────────────────────────────────────────────
\bibliography{ENG_FIT_4701_2.bib}

\end{document}
